Nail: A practical interface generator for data formats

### 2014-11-14 paper/login/abstract.tex
Login first rough draft

\textit{Nail} is a tool that greatly reduces the
programmer effort for safely parsing and generating data formats defined
by a grammar.
Nail introduces several key
ideas to achieve its goal.  First, Nail uses the protocol grammar to
define not just the data format, but also the internal object model
of the data.  Second, Nail eliminates the notion of semantic actions,
used by existing parser generators, which reduces the expressive power
but allows Nail to both {\em parse} data formats and {\em generate}
them from the internal object model, by maintaining a {\em semantic
bijection} between the data format and the object model.  Third,
Nail introduces {\em dependent fields} and {\em stream transforms} to
capture protocol features such as size and offset fields, checksums,
and compressed data, which are impractical to express in existing
protocol languages.  Using Nail, we implement an authoritative  DNS server in
C in under 300 lines of code and grammar, and an {\tt unzip}
program in C in 220 lines of code and grammar, demonstrating that Nail
makes it easy to parse complex real-world data formats.  Performance
experiments show that a Nail-based DNS server can outperform the widely
used BIND DNS server on an authoritative workload,
 demonstrating that systems built with Nail can achieve good
performance.

>>>>

\textit{Nail} is a tool that greatly reduces the
programmer effort for safely parsing and generating data formats defined
by a grammar.
Nail introduces several key
ideas to achieve its goal.  First, Nail uses a protocol grammar to
define not just the data format, but also the internal object model
of the data.  Second, Nail eliminates the notion of semantic actions,
used by existing parser generators, which reduces the expressive power
but allows Nail to both {\em parse} data formats and {\em generate}
them from the internal object model, by establishing a {\em semantic
bijection} between the data format and the object model.  Third,
Nail introduces {\em dependent fields} and {\em stream transforms} to
capture protocol features such as size and offset fields, checksums,
and compressed data, which are impractical to express in existing
protocol languages.  Using Nail, we implement an authoritative  DNS server in
C in under 300 lines of code and grammar, and an {\tt unzip}
program in C in 220 lines of code and grammar, demonstrating that Nail
makes it easy to parse complex real-world data formats.  Performance
experiments show that a Nail-based DNS server can outperform the widely
used BIND DNS server on an authoritative workload,
 demonstrating that systems built with Nail can achieve good
performance.

### 2014-11-14 paper/login/concl.tex
Login first rough draft

This paper presented the design and implementation of \textit{Nail},
a tool for parsing and generating complex data formats based on a
precise grammar.  Nail helps programmers avoid
memory corruption and inconsistency vulnerabilities while reducing effort
in parsing and generating real-world protocols and file formats.
Nail achieves this by reducing the expressive power of the grammar,
establishing a \emph{semantic bijection} between data formats and internal
representations.  Nail captures complex data formats by introducing
\emph{dependent fields}, \emph{streams}, and \emph{transforms}.
Using these techniques, Nail is able to support DNS packet and ZIP file
formats, and enables applications to handle these data formats in many
fewer lines of code.
Nail and all of the applications and grammars developed in this paper
are released as open-source software, available at
\url{https://github.com/jbangert/nail}.

>>>>

 We presented the design and implementation of \textit{Nail},
a tool for parsing and generating complex data formats based on a
precise grammar. This helps programmers avoid
memory corruption and inconsistency vulnerabilities while reducing effort
in parsing and generating real-world protocols and file formats.
 Nail captures complex data formats by introducing
\emph{dependent fields}, \emph{streams}, and \emph{transforms}.
Using these techniques, Nail is able to support DNS packet and ZIP file
formats, and enables applications to handle these data formats in many
fewer lines of code.

Nail and all of the applications and grammars developed in this paper
are released as open-source software, available at
\url{https://github.com/jbangert/nail}. A more detailed discussion of our design and our results is
available in~\cite{bangert:osdi-nail14}.

### 2014-11-14 paper/login/design.tex
Login first rough draft

\section{Design}
\label{s:design}

Nail's goals are to reduce programmer effort required to safely interact with data formats and
prevent vulnerabilities like those described in \S\ref{s:motivation}. In particular, this means:

\begin{itemize}

\item Using a single grammar to define both the \emph{external format} and the
  \emph{internal representation}.  This allows the same grammar to be re-used
  in multiple programs, and helps avoid vulnerabilities like the Android Master
  Key bug.

\item Parsing inputs into internal representations, as well as
      generating outputs from internal representations, without
      requiring the programmer to write any semantic actions. This prevents
      vulnerabilities such as the iOS XNU bug, where format recognition and semantics
      are mixed and interact in unexpected ways.

\item Eliminating redundancy in internal representations, such as
      storing both an explicit length field and an implicit length
      of a container data structure, to provide programmers
      a consistent, unambiguous view of the data.
      This helps avoid bugs such as the one discovered in the
      Python ZIP library~\cite{python-bug:20078}.

\item Allow programmers to define grammars for complex real-world
      data formats through well-defined extensibility mechanisms. 
      This helps prevent programmers from falling back on manual
      parsing when encountering a complex data format.

\end{itemize}

\subsection{Overview}

\paragraph{Internal model.}

Nail grammars describe both the \emph{external format} and an
\emph{internal representation} of a protocol, as opposed to existing
grammar languages, which describe only the former and leave it up to
the programmer to construct an internal representation, typically in
the form of an abstract syntax tree.
Nail produces the following from a single, descriptive grammar:

\begin{CompactItemize}
\item \textit{type declarations} for the internal model,
\item the \textit{parser}, a function to parse a sequence of bytes into an
instance of the model, and
\item the \textit{generator}, a function to create a
sequence of bytes from an instance of the model.
\end{CompactItemize}

For example, Figure~\ref{fig:dns-full} shows an example grammar for DNS packets. Nail produces two
functions shown in Figure~\ref{fig:dns-full-api} that parse a DNS packet into the structures
partially shown in
Figure~\ref{fig:dns-full-struct} and vice versa.

\input{fig-dnsfull}

\noindent

\paragraph{Semantic bijection.}
Parsing inputs and generating outputs form a bijection. However,
a bijection in the traditional sense often does not make sense for data
formats. Consider a grammar for a text language that tolerates white space, or a binary protocol
that tolerates arbitrarily long padding. Program semantics should be independent of the number of padding elements in the input, and Nail therefore
does not expose that information to the programmer. We call such discarded fields \emph{constants}. 
Similarly, programs should not necessarily preserve the layout of objects referred to by their offsets.

Therefore, Nail  maintains only a  \emph{semantic bijection} between the external format and the internal model.
That is, when Nail parses an input into an internal representation, and then
generates output from that representation, the two byte streams (input and
output) will have the same meaning (i.e., be interpreted equivalently by Nail).
However, the byte streams might not be identical. If the grammar
consists of a simple protocol without offset fields, constants, and the like, there is a
conventional bijection between  internal models and valid parser inputs.
%\footnote{Say, the physical layer of most communication
%  protocols is a possibly infinite sequence of symbols that are syntactically nil followed by a
%  pre-determined synchronization sequence and the actual contents of the transmission.}

\paragraph{Hide redundant information.}
Nail's internal model is designed to hide unneeded and redundant information from the application.
Nail introduces \emph{dependent fields}, which contain data that can be computed during generation
and need to be kept as additional state during parsing. Dependent fields are, for example, used to represent
lengths, offsets, and checksums. If dependent fields were exposed in the internal model, information
would be duplicated and inconsistent internal data structures could be produced when data is
modified. For example when using Nail to handle UDP packets, without dependent fields, programmers
might forget to update checksum fields when they modify the payload data.

\paragraph{Parser extensions.}
Real-world protocols contain complicated ways of encoding data. Fully representing these in an
intentionally limited model such as our parser language is impractical. Therefore, Nail introduces
\emph{transformations}, which allow arbitrary code by the programmer to interact with the parser and
generator. Nail parsers and generators interact with data through an abstract stream, which allows
reading and writing of bits as re-positioning. Transformations allow the programmer to write
functions in a general purpose language that consume streams and define new temporary streams, while
also reading or writing the values of dependent fields.

Initial versions of Nail's design included a special combinator for handling offset fields,
which consumed a dependent field and applied
a parser at the offset specified therein. However, it proved impossible to foresee all the ways in which a protocol could encode an offset;
for example, some protocols such as PDF and ZIP locate structures by scanning for a magic number starting at the
end of the file or a fixed offset. In nested grammars, offsets are also not necessarily computed from
the beginning of a file or packet.
Nail's transformations allow the programmer to write arbitrary functions that can
handle such structures and streams, which are a generic abstraction for input and
output data that allow the decoded data to be integrated with the rest of the
generated Nail parser.

\input{fig-syntax}

\subsection{Basics}

A Nail parser defines both the structure of some external format and a data type to represent that
format. Parsers are constructed by combinators over simpler parsers, an approach popularized by the Parsec
framework~\cite{LeijenMeijer:parsec}. We provide the most common combinators familiar from other parser
 combinator libraries, such as Parsec and Hammer~\cite{hammer-parser} and extend them so they also
 describe a data type.

We present both a systematic overview of Nail's syntax with short examples
in Figure~\ref{fig:syntax}, and explain our design in more detail below,
using a grammar for the well-known DNS protocol as a running example
(shown in Figure~\ref{fig:dns-full}).

\paragraph{Parsing.}
\paragraph{Rules.}
A Nail grammar consists of rules that assign a parser to a name. Rules are written as assignments,
such as \cc{ints = /*parser definition*/}, which defines a rule called \cc{ints}. As we will
describe later in \S\ref{s:dependent} and \S\ref{s:transforms}, rules can optionally consume parameters.
Rules can be invoked in a Nail grammar anywhere a parser can appear. Rule invocations act as though
the body of the rule had been substituted in the code. If parameters appear, they are passed by
reference.
\paragraph{Integers and constraints.}

Nail's fundamental parsers represent signed or unsigned
integers with arbitrary lengths up to 64 bits.
Note that is possible to define parsers for sub-byte lengths, for example, the flag bits in the DNS
message header, in lines 4 through 8.

The grammar can also constrain the values of an integer.  Nail expresses
constraints as a set of permissible values or value ranges. Extending the Nail language and
implementation to support richer constraints languages would be relatively trivial, however we have
found that the current syntax covers permissible values within existing protocols correctly and
concisely.

\paragraph{Repetition.}

The \emph{many} combinator takes a parser and applies it repeatedly
until it fails, returning an array of the inner parser's results. In line 39 of the DNS grammar, a
sequence of labels is parsed by parsing as many labels as possible, that is, until an invalid length
field is encountered.
The \emph{sepBy} combinator
additionally takes a constant parser, which it applies in between parsing
two values, but not before parsing the first value or after parsing the
last.  This is useful for parsing an array of items delimited by a separator.
%For examle, \cc{many uint8} represents an array of 8-bit unsigned
%integers, and \cc{sepBy uint8=',' (many uint8 | '0'..'9')} recognizes
%comma-separated lists of decimal numbers.

@@

Nail provides a structure combinator with semantic labels instead of the sequence combinator that
other parser combinator libraries use to capture structures in data formats. 
The structure combinator consists of a sequence of fields, typically consisting of a label and a
parser that describes the contents of that field, surrounded by curly braces. Other field types will be described below.
 The syntax of the structure combinator is inspired by the Go language~\cite{golang}, with field
 names preceding their definition.

% A sample grammar for a DNS header and the corresponding C data type the Nail parser produces, are
% shown in Figure~\ref{fig:dns-struct}.

\paragraph{Constants.}
In some cases, not all bytes in a structure actually contain information, such as magic numbers or
reserved fields. Those fields can be represented in Nail grammars by constant fields in structures.
Constant fields do not correspond to a field in the internal model, but they are validated during
parsing and generated during output.  Constants can either have integer values, such as
in line 9 of the DNS grammar, or string values for text-based protocols, e.g. \cc{many uint8 = ``Foo''}.

In some protocols, there might be many ways to represent the same constant field
and there is no semantic difference between the different syntactic representations.
Nail therefore allows repeated constants, such as \cc{many (uint8=' ')}, which parses any number of space characters, or
\cc{|| uint8 = 0x90 || uint16 = 0x1F0F}, which parses two of the many representations for x86
NOP instructions, which are used as padding between basic blocks in an executable.

As discussed above, choosing to use these combinators on constant parsers
weakens the bijection between the format and the data type, as there are
multiple byte-strings that correspond to the same internal representation and
the generator chooses one of these.

@@

\paragraph{Choices.}
If multiple structures can appear at a given position in a format, the programmer lists the options
along with a label for each in the \cc{choose} combinator. 
During parsing, Nail remembers the current input position and attempts each option in the order they
appear in the grammar. If an option fails, the parser backtracks to the initial position. If no
options succeed, the entire combinator fails. In the data model, choices are represented as tagged
unions.  The programmer has to be careful when options overlap, because if the programmer meant to
generate output for a choice, but the external representation is also valid for an earlier,
higher-priority option, the parser will interpret it as such. However, real data formats normally do
not have this overlap and we did not encounter it in the grammars we wrote.
An example is provided in Figure~\ref{fig:grammar-arith}.

% If two options the same string could be parsed by two options, generated output for the latter
% option is not necessarily understood identically by the parser. However, actual data formats are
% usually not ambiguous in this sense.
% \XXX[nz][I don't understand this paragraph (esp the first sentence).]

\paragraph{Optional.}
Nail includes an \cc{optional} combinator, which attempts to recognize a value, but succeeds
without consuming input when it cannot recognize that value. Syntactically, \cc{optional} is
equivalent to a choice between the parser and an empty structure, but in the internal model it is
more concisely represented as a reference that is null when the parser fails.
For example, the grammar for  Ethernet headers uses \cc{optional vlan\_header} to parse the VLAN
header that only appears in Ethernet packets transmitted to a non-default VLAN\@.

\paragraph{References.}
Rules allow for recursive grammars. To support recursive data types, we allow introduce the
reference combinator \cc{*}  that does not change the syntax of the external format described, but
introduces a layer of indirection, such as a reference or pointer, to the model data type.
The reference combinator does not need to be used when another combinator, such as \cc{optional} or
\cc{many}, already introduces indirection in the data type. An example is shown in Figure~\ref{fig:grammar-arith}.

@@

\subsection{Dependent fields}
\label{s:dependent}
Data formats often contain values that are determined by other values or the layout of information,
such as checksums, duplicated information, or offset and  length fields.
We represent such values using \emph{dependent fields} and handle them transparently during
parsing and generation without exposing them to the internal model.

@@

Dependent fields are handled like other fields when parsing input, but their values are not stored
in the internal data type. Instead the value can be referenced by subsequent parsers and it
discarded when the field goes out of scope.
When generating output, Nail visits a dependent field twice. First, while generating the other fields of a
structure, the generator reserves space for the dependent field in the output. Once
the dependent field goes out of scope, the generator  writes the
dependent field's value to this space.

Nail provides only one built-in combinator that uses dependent fields, \cc{n_of}, which acts like
the \cc{many} combinator, except it represents an exact number, specified in the dependent field, of
repetitions, as opposed as many repetitions as possible. For example, DNS labels, which
are encoded as a length followed by
a value are described in line 38 of the DNS grammar.
Other dependencies, such as offset fields or checksums, are not handled directly by combinators, but
through  transformations, as we describe next.

@@

Nail introduces two concepts to handle these challenges, \emph{streams} and \emph{transformations}. 
Streams represent a sequence of bytes that contain some external format. The parsers and generators
that Nail generates always operate on an implicit stream named \cc{\$current} that they process front to
back, reading input or appending output.
Grammars can use the \cc{apply} combinator to parse or generate external data on a different stream,
inserting the result in the data model.

@@

Transformations need to be carefully written, because they can escape Nail's security and introduce
bugs. However, as we will show in \S\ref{s:eval-effort}, Nail transformations are much shorter than
hand-written parsers and many formats can be represented with just the transformations in the
standard library. 
For example, our Zip transformations are 78 lines of code, compared to 1600 lines of code for a
   hand-written parser. Additionally, Nail provides convenient and safe interfaces for allocating
   memory and accessing streams that address the most common occurrences of buffer overflow
   vulnerabilities.

Transformations can handle a wide variety of patterns in data formats, including the following: 
\paragraph{Offsets.}
A built-in transformation for handling offset fields, which is invoked as follows:
\cc{\$fragment transform offset\_u32(\$current, \cc{@}offset)}. 
This transformation corresponds to two functions for parsing and
generation, as shown in Figure~\ref{fig:xform-sig}. It defines a new stream \cc{\$fragment} that can
be used to parse data at the offset contained in \cc{@offset}, by
using \cc{apply \$fragment some_parser}.

\begin{figure}[h]
\smaller[0.5]
\input{code/offset-xform}
\caption{Pseudocode for two functions that implement the offset transform.}
\label{fig:xform-sig}
\end{figure}

@@

\paragraph{Checksums.}
Checksums can be verified and computed in a transformation that takes a stream and a dependent
field. In some cases, a checksum is calculated over a buffer that contains the checksum itself, with
the checksum being set to some particular value. Because the functions implementing a transformation
are passed a pointer to any dependent fields, the checksum function can set the checksum's initial
value before calculating the checksum over the entire buffer, including the checksum.

\paragraph{}
A real-world example with many different transforms, used to support
the ZIP file format, is described in \S\ref{s:eval-formats}.

>>>>

\section{Design By Example}
In this section, we will explain how to handle basic data formats in Nail, how to handle
redundancies in the format with dependent fields and how Nail parsers can be extended with
transformations.

We will use DNS packets as a leading example, as defined in RFC 1035~\cite[\S4]{RFC:1035}.  Each DNS packet consists of a
header, a set of question records, and a set of answer records. Domain
names in both queries and answers are encoded as a sequence of labels,
terminated by a zero byte.  Labels are Pascal-style strings, consisting
of a length field followed by that many bytes comprising the label.
\label{s:design}
\subsection{Basic Data formats}
\input{fig-dnsfull}
Let's stepping through a simplified Nail grammar for non-compressed
packets, shown in  Figure~\ref{fig:dns-full}.  For this grammar, Nail produces the type declarations
shown in Figure~\ref{fig:dns-full-struct}, and the parser and
generator functions shown in Figure~\ref{fig:dns-full-api}. A more concise reference of the syntax
can be found in~\ref{fig:syntax}.
Nail grammars are reuseable between applications and we will use this grammar to implement
both a DNS server and client, which previously would have had two separate hand-written parsers,
leading to bugs such as  the Android Master Key.

A Nail grammar file consists of rule definitions, for example l. 1-20,  which assign a name
(\texttt{dnspacket}) to a grammar production (2-20). If you are not familiar with
other parsers, you can imagine rules as C type declarations on steroids
(although our syntax is inspired by Go).

Just like C supports various constructs to build up types, such as structures, unions, pointers and
elemental types, Nail supports a integers as elemental parsers and a plethora of \emph{combinators}
to represent features of a file or protocol.

\paragraph{Integers and Constraints}.
Because Nail is designed to cope with binary formats,
it handles not only common integer types (such as \texttt{uint16} on l. 16), but bit fields of any
length, such as \texttt{uint1}. These integers are exposed to the programmer as an appropriately
sized machine integer, e.g. \texttt{uint8\_t}. Nail also supports constraints on integer values,
limiting the values to either a range (l. 23, \texttt{|1..16}), which can optionally be half-open,
or a fixed set (l. 24, \texttt{|[1,255]}). Both types of constraint can be combined, e.g. \texttt{|
  [1..16,255]}. Constant values are also supported, e.g. l. 10: \texttt{uint3=0} represents
three reserved bits that must be 0. Because constant values carry no information, they are not
represented in the data type.

@@

The body of the \texttt{dnspacket} rule is a structure, which contains any number of fields enclosed
between  curly braces. Each field in the structure is parsed in sequence, and represented as a
structure to the programmer.  Contrary to other programming languages, Nail does not have a special
keyword for structs. We also reverse the usual structure-field syntax: \texttt{id uint1} is a field
called \texttt{id} with type \texttt{uint1}\footnote{This is a feature from Go, and makes nested
  types more readable and the parser for Nail itself easier to write.}.

@@

\paragraph{Choices.}
If multiple structures can appear at a given position in a format, the programmer lists the options
along with a label for each in the \cc{choose} combinator. 
During parsing, Nail remembers the current input position and attempts each option in the order they
appear in the grammar. If an option fails, the parser backtracks to the initial position. If no
options succeed, the entire combinator fails. In the data model, choices are represented as tagged
unions.  The programmer has to be careful when options overlap, because if the programmer meant to
generate output for a choice, but the external representation is also valid for an earlier,
higher-priority option, the parser will interpret it as such. However, real data formats normally do
not have this overlap and we did not encounter it in the grammars we wrote.
An example is provided in Figure~\ref{fig:grammar-arith}.
\paragraph{Repetition.}

The \cc{many} combinator takes a parser and applies it repeatedly
until it fails, returning an array of the inner parser's results. In line 39 of the DNS grammar, a
sequence of labels is parsed by parsing as many labels as possible, that is, until an invalid length
field is encountered.
The \cc{sepBy} combinator
additionally takes a constant parser, which it applies in between parsing
two values, but not before parsing the first value or after parsing the
last.  This is useful for parsing an array of items delimited by a separator.
%For examle, \cc{many uint8} represents an array of 8-bit unsigned
\paragraph{Optional.}
Nail includes an \cc{optional} combinator, which attempts to recognize a value, but succeeds
without consuming input when it cannot recognize that value. Syntactically, \cc{optional} is
equivalent to a choice between the parser and an empty structure, but in the internal model it is
more concisely represented as a reference that is null when the parser fails.
For example, the grammar for  Ethernet headers uses \cc{optional vlan\_header} to parse the VLAN
header that appears only in Ethernet packets transmitted to a non-default VLAN\@.

\paragraph{References.}
Rules allow for recursive grammars, but some programming languages, such as C, do not support
recursive structures.  We introduce the
reference combinator \cc{*}  that does not change the syntax of the external format described, but
introduces a reference or pointer to the internal data type.
The reference combinator does not need to be used when another combinator, such as \cc{optional} or
\cc{many}, already introduces indirection in the data type. An example is shown in Figure~\ref{fig:grammar-arith}.

@@

\subsection{Redundant Data}
\label{s:dependent}
Data formats often contain values that are determined by other values or the layout of information,
such as checksums, duplicated information, or offset and  length fields. Exposing such values risks
inconsistencies that could trick the program into unsafe behaviour. Therefore, we represent such values using \emph{dependent fields} and handle them transparently during
parsing and generation without exposing them to the application.

In DNS packets, the packet header contains count fields (\cc{qc},
\cc{ac}, \cc{ns}, and \cc{ar}), which contain the number of questions and answers that follow the
header, which we represent by dependent fields (line 12-15).

@@

Dependent fields are handled like other fields when parsing input, but only stored temporarily
instead of in the data type. Their value can be referenced by other parsers until it goes out of scope.
When generating output, Nail visits a dependent field twice. First, while generating the other fields of a
structure, the generator reserves space for the dependent field in the output. Once
the dependent field goes out of scope, the generator  writes the
dependent field's value to this space.

Nail provides only one built-in combinator that uses dependent fields, \cc{n_of}, which acts like
the \cc{many} combinator, except it parses an exact number of repetitions specified in the dependent
field. Lines 16-19 in Figure~\ref{fig:dns-full} shows how to use \cc{n_of} to parse the question and
answer records in a DNS packet.
Other dependencies, such as offset fields or checksums, are not handled directly by combinators, but
through  transformations, as we describe next.

@@

Nail introduces two concepts to handle these challenges, \emph{streams} and \emph{transformations}. 
Streams represent a sequence of bytes that contain some external format. The parsers and generators
that Nail generates always operate on an implicit stream named \cc{\$current} that they process front to
back, reading input or appending output.
Grammars can use the \cc{apply} combinator to parse a stream or generate output into it.

@@

Transformations need to be carefully written, because they can violate Nail's safety properties
and introduce
bugs. However, as we will show in \S\ref{s:eval-effort}, Nail transformations are much shorter than
hand-written parsers, and many formats can be represented with just the transformations in Nail's
standard library.
For example, our Zip transformations are 78 lines of code, compared to 1600 lines of code for a
   hand-written parser. Additionally, Nail provides convenient and safe interfaces for allocating
   memory and accessing streams that address the most common occurrences of buffer overflow
   vulnerabilities.

Transformations can handle a wide variety of patterns in data formats, including the following:

For example, DNS uses label compression to reduce the overhead of including each domain name
multiple times in a DNS reply. If a domain name suffix is repeated, it may be replaced by a two-bit
marker followed by a  14-bit offset into the packet, indicating the position where that suffix was
previously encoded.  We use a transform in line 35
of our DNS grammar to handle DNS label compression; the signatures of the two transform functions are shown
in Figure~\ref{fig:dns-xform}.  When parsing a packet, this transform
decompresses the DNS label stream.
When generating a packet, this transform receives the current suffix as
an input, and scans the packet so far for previous occurrences and inserts the offset.

Handling label compression in existing tools, such as Bison or Hammer,
would be awkward at best, because some ad-hoc trick would have to
be used to re-position the parser's input stream.  Keeping track of the
position of all recognized labels would not be enough, although still awkward, as the offset field
may refer to any byte within the packet.
For this reason, the sample DNS grammar in Hammer does not
support compression.

\paragraph{Offsets.}
A built-in transformation for handling offset fields, which is invoked as follows:
\cc{\$fragment transform offset\_u32(\$current, \cc{@}offset)}. 
This transformation corresponds to two functions for parsing and
generation, as shown in Figure~\ref{fig:xform-sig}. It defines a new stream \cc{\$fragment} that can
be used to parse data at the offset contained in \cc{@offset}, by
using \cc{apply \$fragment some_parser}.

@@

\paragraph{Checksums.}
Checksums can be verified and computed in a transformation that takes a stream and a dependent
field. In some cases, a checksum is calculated over a buffer that contains the checksum itself, with
the checksum being set to some particular value.

\paragraph{}
A real-world example with many different transforms, used to support
the ZIP file format, is described in our full paper.%\S\ref{s:eval-formats}.
